Bootstrap Confidence Intervals for Regression Discontinuity Designs with Uniform Kernels

### 2016-02-28 main_paper.tex
Minor changes to introduction. Gray, please check if I did not say anything stupid. I also over played the cross sectional dependence case a little more as a future research topic since people seen to be interested in it.

But, as \cite{calonico2014}\footnote{%
  We will refer to \cite{calonico2014} frequently, so we will reference it as
  ``CCT'' for the rest of the paper.} %
point out, the \cite{IK} bandwidth estimator has the serious drawback that,
although it is AMSE-optimal for point estimation, it produces invalid
\emph{confidence intervals} and hypothesis tests. The AMSE-optimal bandwidth
converges to zero slowly, so the remaining bias term is large enough to affect
the asymptotic distribution of the estimator. In that case the usual ``naive''
confidence intervals for the RD treatment effects may be biased can have
coverage well below their nominal level. CCT then make two contributions: first,
they propose an estimator of the bias resulting from undersmoothing and provide
a treatment effect estimator that remains asymptotically unbiased even when the
bandwidth converges to zero slowly, at the AMSE-optimal rate.  Second, since
this bias-correction term contributes to the asymptotic variance of the
resulting treatment effect estimator, CCT also provide a new formula for its
asymptotic variance. The resulting confidence intervals have accurate coverage
even when the naive RD interval does not.

In this paper, we propose a bootstrap alternative to CCT's analytical
corrections. CCT justify their estimator by showing that the bias and variance
components for a local linear model can be accounted for by estimating a local
second order polynomial with bandwidth of the same order.\footnote{%
  More generally, they show that the bias and variance of a local polynomial of
  order $p$ can be accounted for by estimating the $p+1$ local polynomial. We
  will restrict our analysis to the case with $p = 1$ in this paper because
  of its widespread use.} %
They use a Taylor expansion around the cutoff to show that the bias associated
with the second order polynomical converges to zero at a faster rate, fast
enough that the bias of the local linear model can be estimated and removed
using the second order polynomial. The second order polynomial also provides
fast enough convergence that it can be used to estimate the correct variance
correction as well.

Our approach exploits CCT's theoretical insight through a new residual
bootstrap. In particular, we propose, after estimating the local linear model as
usual, estimating a local second order polynomial and generating bootstrap
datasets by resampling the residuals of that polynomial. Since the second order
polynomial is the true Data Generating Process (DGP), its estimate of the
treatment effect is the true value of the treatment effect under the
distribution induced by this bootstrap. The bias of the linear model is known
under this distribution and can be calculated by averaging the error of the
linear model's estimates across many bootstrap replications. This approach is
described in detail by our Algorithm~\ref{Alg1} and the resulting bias corrected
estimator is shown to be asymptotically normal with mean zero in our
Theorem~\ref{T1} under AMSE-optimal bandwidth rates.

@@

This bootstrap procedure can offer some advantages over analytical methods in
this setting. In particular, both this paper and CCT assume that the
observations are generated independently of each other; extending these bias
correction methods to other forms of dependence is relatively straightforward
for the bootstrap but can be substantially more complicated for analytical
corrections, which have to be explicitly derived by the researcher. Similarly,
although we only provide results for the local linear model in this paper, it is
trivial to implement this procedure for higher order polynomials, for
covariate-adjusted estimators \citep{calonico2015}, or for other local
smoothers. \citep{loader2006} However, in this paper we focus on the baseline
case of sharp RD with a local linear model and uniform kernel. Extensions to
fuzzy RD and nonuniform kernels, which require nontrivial changes to the
underlying bootstrap algorithm, are the subject of ongoing research.

>>>>

But, as \cite{calonico2014}\footnote{%
  We will refer to \cite{calonico2014} frequently, so we will reference it as
  ``CCT'' for the rest of the paper.} %
point out, the \cite{IK} bandwidth estimator has the serious drawback that,
although it is AMSE-optimal for point estimation, it produces invalid
\emph{confidence intervals} and hypothesis tests. The AMSE-optimal bandwidth
converges to zero slowly, so the remaining bias term is large enough to affect
the asymptotic distribution of the estimator. In that case the usual ``naive''
confidence intervals for the RD treatment effects may be biased and have
coverage well below their nominal level. CCT then make two contributions: first,
they propose an estimator of the bias resulting from undersmoothing and provide
a treatment effect estimator that remains asymptotically unbiased even when the
bandwidth converges to zero slowly, at the AMSE-optimal rate.  Second, since
this bias-correction term contributes to the asymptotic variance of the
resulting treatment effect estimator, CCT also provide a new formula for its
asymptotic variance. The resulting confidence intervals have accurate coverage
even when the naive RD interval does not.

In this paper, we propose a bootstrap alternative to CCT's analytical
corrections. CCT justify their estimator by showing that the bias and variance
components for a local linear model can be accounted for by estimating a local
second order polynomial with bandwidth of the same order.\footnote{%
  More generally, they show that the bias and variance of a local polynomial of
  order $p$ can be accounted for by estimating the $p+1$ local polynomial. We
  will restrict our analysis to the case with $p = 1$ in this paper because
  of its widespread use.} %
They use a Taylor expansion around the cutoff to show that the bias associated
with the second order polynomial converges to zero at a faster rate, fast
enough that the bias of the local linear model can be estimated and removed
using the second order polynomial. The second order polynomial also provides
fast enough convergence that it can be used to estimate the correct variance
correction as well.

Our approach exploits CCT's theoretical insight through a new residual
bootstrap. In particular, we propose, after estimating the local linear model as
usual, estimating a local second order polynomial and generating bootstrap
datasets by resampling the residuals of that polynomial. Since the second order
polynomial is the true Data Generating Process (DGP) in the bootstrapped data, its estimate of the
treatment effect is the true value of the treatment effect under the
distribution induced by this bootstrap. The bias of the linear model is known
under this distribution and can be calculated by averaging the error of the
linear model's estimates across many bootstrap replications. This approach is
described in detail by our Algorithm~\ref{Alg1} and the resulting bias corrected
estimator is shown to be asymptotically normal with mean zero in our
Theorem~\ref{T1} under AMSE-optimal bandwidth rates.

@@

This bootstrap procedure can offer some advantages over analytical methods in
this setting. In particular, both this paper and CCT assume that the
observations are generated independently of each other; extending these bias
correction methods to other forms of dependence is relatively straightforward
for the bootstrap but can be substantially more complicated for analytical
corrections, which have to be explicitly derived by the researcher. Similarly,
although we only provide results for the local linear model in this paper, it is
trivial to implement this procedure for higher order polynomials, for
covariate-adjusted estimators \citep{calonico2015}, or for other local
smoothers. \citep{loader2006} However, in this paper we focus on the baseline
case of sharp RD with a local linear model and uniform kernel. Extensions to
fuzzy RD and nonuniform kernels, which require nontrivial changes to the
underlying bootstrap algorithm, as well as developments to address cross sectional dependence,
 are the subject of ongoing research.
